\mytitle{}

### 2018-08-30 paper/paper.tex
More paper work.

%% Fix indent in new section...
\newcommand{\subparagraph}{}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{1.5ex}{0.7ex}
\titlespacing*{\subsection}{0pt}{1.5ex}{0.7ex}
%\titleformat*{\filcenter\scshape}

@@

\section{Performance in an Emulated Environment}\label{sec:performance-in-an-emulated-environment}
The original introduction of this approach to direct-control reinforcement learning as introduced by \textcite{DBLP:journals/eaai/MalialisK15} fails to consider key cases: disjoint ranges of traffic distribution (i.e., the presence of benign heavy-hitters), the accurate simulation of TCP-like behaviour (and its effects on collateral damage), and assumes a rigid ISP-like topology.
The latter two are most deserving of a closer investigation, as they have stronger implications for wide-scale deployment.

@@

?? TODO: Gut this section now...
While Tcpreplay was useful in recreating the original work and examining the above condition, flow behaviour under packet loss is closer to that of UDP when using it to replay traffic.
To investigate the effects of collateral damage upon benign TCP flows, an iperf3 test was conducted using mininet.
Several hosts communicated concurrently to a single server over one switch, with maximum send rates in $\{1,...,5\}$ \si{\mega\bit\per\second} and a constant \SI{40}{\milli\second} latency.
The rate of packet drop was increased linearly from \SIrange{0}{40}{\percent} and the observed throughput for each host was measured, to show a trend and determine for the mininet environment whether throughput would decrease as expected, at a super-linear rate.

@@

\begin{figure}
	\includegraphics[width=\linewidth]{../plots/online-varyN-nginx}
	\caption{
		A more convincing and/or to-the-point figure for getting people to believe I'm doing god's work.
		\label{fig:nginx-coffin-nail}
	}
\end{figure}

@@

The performance characteristics of TCP under packet drop  are well-known and well-understood through the Mathis equation \cite{DBLP:journals/ccr/MathisSMO97}:
\begin{equation}
\operatorname{BW} = \frac{\operatorname{MSS}}{\operatorname{RTT}} \frac{C}{\sqrt{p}},
\end{equation}
for the \emph{maximum segment size} (MSS), \emph{round trip time} (RTT), a choice of constant $C \approx{} \sqrt{3/2}$ dependent on system assumptions, and the probability $p \in (0, 1]$ that a packet is lost.
%The lower bound on $p$ is deliberately open, as packet drop acts as a control signal for the TCP send window size and is an expected part of normal operation.
TCP flows in Mininet are found to obey this law, as expected.
This reveals that the original work \emph{does not capture this behaviour}, or else the initial experiment (UDP-like traffic when $n=2$) wouldn't have achieved similar results to those which were reported.

@@

\section{A New Normal}

?? Full Openflow controller setup (in mininet)
?? TODO: everything

@@

@@

@@

\section*{Acknowledgements}
My thanks go to Mircea Iordache and Richard Cziva for their comments and technical assistance.
Additional thanks \emph{would} go out to my anonymous reviewers, had I any of them.

>>>>

%% Fix indent in new section...
\newcommand{\subparagraph}{}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{1.5ex}{0.7ex}
\titlespacing*{\subsection}{0pt}{1.5ex}{0.7ex}
\titlespacing*{\paragraph}{0pt}{1.5ex}{0.7ex}
%\titleformat*{\filcenter\scshape}

\usepackage{enumitem}
\setlist[description]{leftmargin=8em,style=nextline}

@@

\section{Performance in an Emulated Environment}\label{sec:performance-in-an-emulated-environment}
The original introduction of this approach to direct-control reinforcement learning as introduced by \textcite{DBLP:journals/eaai/MalialisK15} fails to consider key cases: disjoint ranges of traffic distribution (i.e., the presence of benign heavy-hitters), the accurate simulation of TCP-like behaviour (and its effects on collateral damage), and assumes a rigid and unrepresentative topology.
The latter two are most deserving of a closer investigation, as they have stronger implications for wide-scale deployment.

@@

?? TODO: Gut this section now...
%While Tcpreplay was useful in recreating the original work and examining the above condition, flow behaviour under packet loss is closer to that of UDP when using it to replay traffic.
%To investigate the effects of collateral damage upon benign TCP flows, an iperf3 test was conducted using mininet.
%Several hosts communicated concurrently to a single server over one switch, with maximum send rates in $\{1,...,5\}$ \si{\mega\bit\per\second} and a constant \SI{40}{\milli\second} latency.
%The rate of packet drop was increased linearly from \SIrange{0}{40}{\percent} and the observed throughput for each host was measured, to show a trend and determine for the mininet environment whether throughput would decrease as expected, at a super-linear rate.

@@

\begin{figure}
	\includegraphics[width=\linewidth]{../plots/online-varyN-nginx}
	\caption{
		A more convincing and/or to-the-point figure for getting people to believe I'm doing god's work.
		?? TODO: describe 4 real.
		\label{fig:nginx-coffin-nail}
	}
\end{figure}

@@

?? Quic will probably behave much like TCP.

The performance characteristics of TCP under packet drop are well-known and well-understood through the Mathis equation \cite{DBLP:journals/ccr/MathisSMO97}:
\begin{equation}
\operatorname{BW} = \frac{\operatorname{MSS}}{\operatorname{RTT}} \frac{C}{\sqrt{p}},
\end{equation}
for the \emph{maximum segment size} (MSS), \emph{round trip time} (RTT), a choice of constant $C \approx{} \sqrt{3/2}$ dependent on system assumptions, and the probability $p \in (0, 1]$ that a packet is lost.
%The lower bound on $p$ is deliberately open, as packet drop acts as a control signal for the TCP send window size and is an expected part of normal operation.
%TCP flows in Mininet are found to obey this law, as expected.
This reveals that the original work \emph{does not capture this behaviour}, or else the initial experiment (UDP-like traffic when $n=2$) wouldn't have achieved similar results to those which were reported.

\Cref{sec:a-new-normal} is where the new normal model arrives. Wow!

\subsection{Computational Cost}
?? Consider talking about the execution times of the old MARL approach here? They're real nice (as expected), so we have lots of room to play around with while (hopefully) remaining under the 1ms target time given by \textcite{DBLP:conf/sigcomm/ChenL0L18}.

We're in \SIrange{80}{100}{\micro\second}

@@

\section{A New Normal}\label{sec:a-new-normal}

In establishing...

?? How will I structure this?
?? Motivation -> Model -> Results?
?? OR Use the results of the last section to springboard into here?

?? Remember, the motivation is clear. We don't care so much that it is "representative" wrt a specific deployment location or network type. The whole purpose of this is that we aim to test specific behaviour which traces cannot replicate (i.e., correlated back-and-forth, dynamics introduced to congestion-aware protocols, ...)
?? If we need to, we can codition the distribution of requests according to statistics mined form an existing trace if reviewer number 2 needs that extra push to be convinced.

?? Full Openflow controller setup (in mininet). All internal routers are primed with knowledge of the shortest path to any internal host, while new inbound flows register the ``way back'' for each hop used to maintain consistency over traffic conditions.
If such information is lost, it suffices to forward an outbound packet on a random (outbound) port, as we assume that any external IP is reachable through any of the test network's egress ports (i.e., that it is not connected to any stub autonomous systems).
The controller is also responsible for responding to ARP traffic, as a gateway might
The necessity of this arises due to the realities of relying upon Linux's IP stack, and would not need to be considered for purely trace-based evaluation.
?? Legitimate traffic: TCP traffic (HTTP clients downloading web pages, dependent resources and files) with a mixture of lifetimes for each request.
?? Malicious traffic: UDP flood traffic (hping3, MTU-size packets, ). Why not min-size packets? Because the traffic generator gets in a horrible rut if I do so...

\Cref{fig:nginx-coffin-nail} shows the effects of using

?? Actually describe what I have here, now. I can do this.

@@

?? What do we want?

\begin{IEEEdescription}[\IEEEsetlabelwidth{Global state}]
	\item[Global state] space space space
	\item[Local state]
\end{IEEEdescription}

\textbf{Global state}---what came before (load statistics from various network locations)

\textbf{Local state}---per-flow data.

?? Last action taken: encodes the notion of current belief of flow maliciousness (default at 0). Potentially allows forgiveness: a mistakenly malicious flow 's falloff after punishment could be used for such purpose (if we're lucky...)

?? Correspondence ratio: ratio (in bytes) between upstream/downstream traffic for a src/dst pair. (Cite the work that suggested this)

?? Source IP, port, protocol (*zzz*)

?? Flow duration, size

?? Change in send/recv rates since last action/check?

?? More things... (look into other works, actually research this...)

\paragraph{Done with that...}

@@

?? What might we do for a reward function in the absence of heuristic estimates and/or explicit a priori knowledge? I think a good candidate is the sum of up and down throughputs (normalised by capacity sum), so long as \emph{neither exceeds the link capacity}. We can extend the team-based formulations similarly. This, in theory, promotes traffic diversity since it's not like flooding-based DDoS attacks are going to submit meaningful work to a server. The intuition, I suppose, is that certain classes of flow will have a small footprint in one direction which causes a sizeable increase in the other!

@@

?? More future work --- share knowledge between agents. ``Knowledge bases'' for this purpose? (see: Qianru).

\section*{Acknowledgements}
My thanks go to Mircea Iordache, Qianru Zhou, and Richard Cziva for their comments and technical assistance.
Additional thanks \emph{would} go out to my anonymous reviewers, had I any of them.
